Reasoning About a Machine with Local Capabilities

### 2018-05-11 toplas/paper.tex
Updated awk. example proof sketch (possible compile error fixed)

  \footnote{We will ignore step indexes in this proof sketch.}then the $\observations$-relation ensures that a successfully halting configuration terminates in a memory that respects a private future world of $W$.
  In $W$ the flag region is permanent, so it guarantees that it will remain unchanged.

@@

  In $W_2$, we replace the stack region with a temporary static region that governs our stack frame including the private registers we push to the stack and the stack recovery code as well as a standard region $\iote^{pwl}$-region for the remainder of the stack.

@@

  \end{proof}
\end{toplas}

  The complete proof can be found in the technical appendix~\citep{technical_appendix}.
\end{toplas}
% As explained in \sectionname~\ref{sec:stack-and-return-pointer}, the
% macro-instruction \texttt{\footnotesize{reqglob $r_1$}} checks that the callback
% is global, essentially to make sure it is not allocated on the stack where it
% might contain old stack pointers or return pointers. Otherwise, the
% encapsulation of our local stack frame could be broken. In the proof of
% Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
% callback in a world that is only a private future world of the one where we
% received the callback, precisely because we have invalidated the adversary's
% local state (particularly their old stack and return capabilities). The callback
% is still valid in this private future world, but only because we know that it is
% global.

>>>>

  \footnote{We will ignore step indexes in this proof sketch.}then the $\observations$-relation ensures that a successfully halting configuration terminates in a memory that respects a private future world of $W$ which in particular means that it respects the permanent static region that governs the assertion flag.

@@

  In $W_2$, we replace the stack region with a temporary static region that governs our stack frame including the private registers we push to the stack and the stack recovery code as well as a standard region $\iota^{pwl}$-region for the remainder of the stack.

@@

  The complete proof can be found in the technical appendix~\citep{technical_appendix}.
  \end{proof}
\end{toplas}
% As explained in \sectionname~\ref{sec:stack-and-return-pointer}, the
% macro-instruction \texttt{\footnotesize{reqglob $r_1$}} checks that the callback
% is global, essentially to make sure it is not allocated on the stack where it
% might contain old stack pointers or return pointers. Otherwise, the
% encapsulation of our local stack frame could be broken. In the proof of
% Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
% callback in a world that is only a private future world of the one where we
% received the callback, precisely because we have invalidated the adversary's
% local state (particularly their old stack and return capabilities). The callback
% is still valid in this private future world, but only because we know that it is
% global.
